### 2019-02-14 Sections/costs_and_attributes_in_quantum_networks.tex
minor

The von Neuman entropy\index{von Neuman entropy} \cite{???} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \log_2 (\lambda_x) \nonumber \\
&= -\mathrm{tr}(\hat\rho\,\log \,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition\index{Spectral decomposition}). In that case, the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\end{figure}

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from 
% \captionspacefig \caption{A sequence of events \mbox{$X\to Y\to Z$}.
 The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).%}%\label{fig:data_proc_ineq}	
which they would like to extract maximal correlations (i.e joint information). 
They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their quantum mutual information of the channel is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\rho,\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B). \label{eq:quant_mut}
\end{align}

>>>>

The von Neuman entropy\index{von Neuman entropy} \cite{bengtsson2017geometry} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \log_2 (\lambda_x) \nonumber \\
&= -\mathrm{tr}(\hat\rho\,\log \,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition\index{Spectral decomposition}). In that case, the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\captionspacefig \caption{\label{fig:data_proc_ineq}A sequence of events \mbox{$X\to Y\to Z$}.
 The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).}	
\end{figure}

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from 
% 
which they would like to extract maximal correlations (i.e joint information). 
They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their quantum mutual information of the channel is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\rho,\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B). \label{eq:quant_mut}
\end{align}
